An Exposition on the Propriety of Restricted Boltzmann Machines

### 2016-07-28 presentations/jsm2016/index.Rmd
clearer images

<div class="double">
<p class="double-flow">
Restricted Boltzmann machine (RBM), which consists of two layers - a hidden ($\mathcal{H}$) and a visible ($\mathcal{V}$).
</p>
<p class="double-flow">
<img src="images/rbm.png" class="one-col-image"></br>
</p>
</div>
<img src="images/visibles_image.png"></br>
Image classification using a RBM. Each image pixel comprises a node in the visible layer, $\mathcal{V}$. The output is used to create features which are then passed to a supervised learning algorithm [@friedman2001elements].

@@

<div class="double">
<p class="double=flow">
"Deep Boltzmann machine" - multiple single layer restricted Boltzmann machines with the lower stack hidden layer acting as the visible layer for the higher stacked model
</p>
<p class="double-flow">
<img src="images/deep_rbm.png"></br>
</p>
</div><br/>

@@

<div class="double">
<p class="double-flow">
<img src="images/toyhull_top.png">
<img src="images/toyhull_top_2.png">
</p>
<p class="double-flow">
Convex hulls of the statistic space for a toy RBM with $V = H = 1$ for $\{0,1\}$-encoding and $\{-1,1\}$-encoding enclosed by an unrestricted hull of 3-space.
</p>
</div>

>>>>

<div class="double">
<p class="double-flow">
Restricted Boltzmann machine (RBM) with two layers - hidden ($\mathcal{H}$) and visible ($\mathcal{V}$) [@friedman2001elements].
</p>
<p class="double-flow">
<img src="images/rbm.png" width="100%"></br>
</p>
</div>
<img src="images/visibles_image.png" width="100%"></br>
Used for image classification. Each image pixel is a node in the visible layer. The output creates features, passed to supervised learning.

@@

<div class="double">
<p class="double=flow">
"Deep Boltzmann machine" - multiple single layer restricted Boltzmann machines with the lower stack hidden layer acting as the visible layer for the higher stacked model
</p>
<p class="double-flow">
<img src="images/deep_rbm.png" width="100%"></br>
</p>
</div><br/>

@@

<div class="double">
<p class="double-flow">
<img src="images/toyhull_top.png" width="100%">
</p>
<p class="double-flow">
<img src="images/toyhull_top_2.png" width="70%">
</p>
</div>

Convex hulls of the statistic space for a toy RBM with $V = H = 1$ for $\{0,1\}$ and $\{-1,1\}$-encoding enclosed by an unrestricted hull of 3-space.

## Data coding to mitigate degeneracy (cont'd)
